%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Finacy} % Organization
{Remote} % Location
{Jun. 2023 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{Led the development of dynamic, user-centric web applications using Typescript, React, and Next.js, driving significant user engagement and satisfaction.}
    \item{Implemented and deployed highly interactive, responsive web pages, focusing on optimizing user experience and interface design.}
    \item {Managed and optimized the infrastructure across AWS, Heroku, and Vercel to ensure high availability and scalability for all company services.}
    \item{Developed and maintained CI/CD pipelines using GitHub Actions, achieving automated deployments and seamless integration processes for various services.}
    \item{Designed and implemented robust backend solutions using Node.js, Express, and MongoDB, focusing on efficiency and scalability.}
    \item{Spearheaded the development of microservices architectures, utilizing Python and FastAPI to enhance modularity and facilitate easier maintenance.}
    \item{Integrated advanced AI technologies into backend systems, significantly improving data processing capabilities and service personalization.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{PublicSquare} % Organization
{Remote} % Location
{Jun. 2023 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {PublicSquare is a budding venture studio. We're always hiring for talented technologists looking to work on mission-driven ventures.}
    \item {Our first venture is Finacy, with a mission of bringing engaging financial education and financial products to families across the US, to help young people grow into financially healthy adults.}
  \end{cvitems}
}




%---------------------------------------------------------
\cventry
{Frontend Developer} % Job title
{Mobills} % Organization
{Ceará, Brazil} % Location
{Mar. 2021 - Dec. 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked on many new features,
    refactors and bug fixes on Mobills
    web platform, using React, Redux
    and Redux Saga}
    \item {Personalized Zendesk templates
    using Vanilla JS and CSS for
    Mobills Help Center}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Pax Insurance Broker} % Organization
    {Ceará, Brazil} % Location
    {Mar. 2021 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a system to manage costumer's Health Insurance changes}
        \item {Developed various systems in order to automate many company's internal processes using Python and Pandas}
        \item {Created Power Bi panels for business presentations}
        \item {Developed a database to store
        all costumer's data}
      \end{cvitems}
  }

\end{cventries}
