%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Finacy} % Organization
{Remote} % Location
{Jun. 2023 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Lead the development of the Finacy game and overall application (MERN stack with Godot for the game engine)}
    \item {Manage all DevOps for the application infrastructure, test environments, including CI/CD}
    \item {Participate in team planning meetings, product roadmap discussions, provide technical advisory based on proposed features and more}
    \item {Finacy is the financial literacy app for kids. In an ever more complicated financial world, teaching kids the money principles that will ensure they're set up for a financial sound future is more important than ever!}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{PublicSquare} % Organization
{Remote} % Location
{Jun. 2023 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {PublicSquare is a budding venture studio. We're always hiring for talented technologists looking to work on mission-driven ventures.}
    \item {Our first venture is Finacy, with a mission of bringing engaging financial education and financial products to families across the US, to help young people grow into financially healthy adults.}
  \end{cvitems}
}



%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Pax Insurance Broker} % Organization
    {Ceará, Brazil} % Location
    {Mar. 2021 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a system to manage costumer's Health Insurance changes}
        \item {Creation of Power Bi panels for business presentations}
        \item {Developed a database to store
        all costumer's data}
        \item {Development of various systems in order to automate many company's internal processes using Python ans Pandas}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {Mobills} % Organization
    {Ceará, Brazil} % Location
    {Mar. 2021 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on many new features,
        refactors and bug fixes on Mobills
        web platform, using React, Redux
        and Redux Saga}
        \item {Personalized Zendesk templates
        using Vanilla JS and CSS for
        Mobills Help Center}
      \end{cvitems}
    }

\end{cventries}
