%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Perkup} % Organization
{Remote (United States)} % Location
{May. 2024 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{Crafted complex SQL queries for data retrieval and analysis using Google BigQuery, enhancing data-driven decision-making processes.}
    \item{Assisted in maintaining Stripe integration for secure and efficient payment processing, improving the overall user transaction experience.}
    \item{Utilized Firebase for backend services, including authentication, real-time database, and cloud functions, to build robust and scalable applications.}
    \item{Contributed to the development and maintenance of a Next.js public catalog for browsing swag and gift items, ensuring a seamless user experience and optimal performance.}
    \item{Collaborated with cross-functional teams to deliver high-quality software solutions, adhering to best practices and industry standards.}
    % 
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{PublicSquare} % Organization
{Remote (Canada)} % Location
{Jun. 2023 - May 2024} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Managed and optimized the infrastructure across AWS, Heroku, and Vercel to ensure high availability and scalability for all company services.}
    \item{Developed and maintained CI/CD pipelines using GitHub Actions, achieving automated deployments and seamless integration processes for various services.}
    \item{Designed and implemented robust backend solutions using Node.js, Express, and MongoDB, focusing on efficiency and scalability.}
    \item{Spearheaded the development of microservices architectures, utilizing Python and FastAPI to enhance modularity and facilitate easier maintenance.}
    \item{Integrated advanced AI technologies into backend systems, significantly improving data processing capabilities and service personalization.}
    \item{Led the development of dynamic, user-centric web applications using Typescript, React, and Next.js, driving significant user engagement and satisfaction.}
    \item{Implemented and deployed highly interactive, responsive web pages, focusing on optimizing user experience and interface design.}
    % 
  \end{cvitems}
}



%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Pax Insurance Broker} % Organization
    {Cear치, Brazil} % Location
    {Mar. 2021 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a system to manage custumer's Health Insurance changes}
        \item {Developed various systems in order to automate many company's internal processes using Python and Pandas}
        \item {Created Power Bi panels for business presentations}
        \item {Developed and maintained a PostgreSQL a database to store
        all custumer's data}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {Mobills} % Organization
    {Cear치, Brazil} % Location
    {Mar. 2021 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on many new features,
        refactors and bug fixes on Mobills
        web platform, using React, Redux
        and Redux Saga}
        \item {Personalized Zendesk templates
        using Vanilla JS and CSS for
        Mobills Help Center}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Freelance Developer} % Organization
{Cear치, Brazil} % Location
{2019 - 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Freelance project development, using technologies such as Node.Js, Python, Bash Scripts, React.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Teacher} % Job title
{Fortaleza City Hall} % Organization
{Cear치, Brazil} % Location
{2019 - 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Taught Mathematics and Physics subjects to 9th grade students for classes for IFCE technical school.}
  \end{cvitems}
}

\end{cventries}
