%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


% %-------------------------------------------------------------------------------
% %	CONTENT
% %-------------------------------------------------------------------------------

\begin{cvparagraph}
Throughout my career, I have actively engaged in a variety of open-source and freelance projects, each presenting unique challenges and learning opportunities.
\end{cvparagraph}

\begin{cvparagraph}
Below, I highlight some of the key projects that best demonstrate my skills and contributions. 
These experiences have honed my ability to deliver innovative, high-quality software solutions in diverse environments.
\end{cvparagraph}



%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Freelance Developer} % Job title
{Hypamaps} % Organization
{Remote (UK)} % Location
{2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    Hypamaps was my first commercial project in an English-speaking environment, presenting a steep learning curve and significant challenges.
    \newline
    As a solo developer, I was responsible for the end-to-end development of a web-based 3D interactive map.
    \newline
    Utilizing TypeScript and Three.js for the frontend, and Python with FastAPI for the backend, I integrated PostgreSQL for data management and deployed the application on Azure.
  \end{cvitems}
}


\cventry
{Open source Developer} % Job title
{Simple Wireplumber GUI} % Organization
{} % Location
{2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    I initiated the 'Simple Wireplumber GUI' project, a user-friendly graphical interface designed to manage audio inputs and outputs on modern Linux systems.
    \newline
    This open-source solution aims to simplify Linux audio configuration, leading to over 10,000 downloads on Flathub.
    \newline
    The community engagement was overwhelmingly positive, resulting in contributions such as translations into Turkish and Dutch, enhancing its usability and accessibility. 
    % 
  \end{cvitems}
}

\cventry
{Open source Developer} % Job title
{Firefox GNOME theme} % Organization
{} % Location
{2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    I contributed to the 'Firefox GNOME theme,' a widely acclaimed project that implements CSS modifications to integrate Firefox's visual design with the GNOME desktop environment.
    \newline
    My involvement, though brief, focused on enhancing specific aspects of the theme's compatibility and install process, ensuring a seamless user experience.
    % 
  \end{cvitems}
}

\end{cventries}


% %---------------------------------------------------------
